% Section 6: Limits and explicit non-claims

This section is placed before reproducibility deliberately. The shortest
honest summary of this artifact is the list of things it does not do.

\subsection{This artifact does NOT contain a new proof}

Theorem~1.1 of \cite{OpenAI2026Proof,Sawin2026Remarks} is proved by
those authors. The present paper does not re-derive Lemma~2.1,
Lemma~2.2, Proposition~2.3, or any other intermediate result. Where the
source papers say ``by the Golod--Shafarevich theorem'' or ``by the
Hajir--Maire tower-cutting argument'', we likewise take those classical
results as given.

\subsection{This artifact does NOT construct the infinite tower}

The existence of $L_j$ with $[L_j : \Q] \to \infty$ and bounded root
discriminant is supplied by Golod--Shafarevich
\cite{GolodShafarevich1964} together with the Hajir--Maire splitting
technique \cite{HajirMaire2001} adapted to pro-$2$ in
\cite{Sawin2026Remarks}. This is a non-constructive existence theorem.
No finite computation can exhibit the entire infinite tower. Phase~3
of the artifact stops at the boundary of computable
admissibility.

\subsection{This artifact has NOT been peer-reviewed}

No external mathematician has reviewed this code base. The grounds on
which a reader might choose to take the artifact's output at face value
reduce to the following three internal checks --- none of which is a
substitute for peer review:

\begin{enumerate}[leftmargin=*]
  \item the $60$-test unit suite passes on CI (Ubuntu + Windows
        $\times$ Python 3.11 / 3.12);
  \item the central numerical reproduction in \S\ref{sec:eq22} matches
        the published value $\approx 6.24 \cdot 10^{-38}$ to a relative
        error of $1.4 \cdot 10^{-4}$, consistent with the
        two-significant-figure rounding in the source;
  \item the source is small (\(\approx\) 1\,000 lines across four
        modules) and intended to be readable cover-to-cover by anyone
        who has read \S2 of \cite{Sawin2026Remarks}.
\end{enumerate}

We treat the artifact as input to mathematician review, not as a
substitute for it.

\subsection{Reported $0.014$ and $0.0318$ are NOT in either formal PDF}

Secondary coverage (e.g.\ \cite{KalaiBlog2026}) reports numerical
values $\delta \approx 0.014$ and $\delta \approx 0.0318$ in the
informal contexts $n^{1.014}$ and $n^{1.0318}$. We verified by direct
text extraction with \texttt{pypdf} that neither of these literal
numerical values appears in either
\cite{OpenAI2026Proof} or \cite{Sawin2026Remarks}. The only rigorous
numerical lower bound that appears verbatim in either formal PDF is
$\delta_{\text{excess}} \approx 6.24 \cdot 10^{-38}$ from eq.~(2.2) of
\cite{Sawin2026Remarks}.

The artifact records this three-way provenance in a small registry
of tagged \texttt{SOURCE\_CLAIMS} entries:

\begin{itemize}[leftmargin=*]
  \item \tname{openai_index_reported} ($\delta = 0.014$), flagged as
        not literally present in either formal PDF;
  \item \tname{sawin_rigorous_lower_bound}
        ($\delta = 6.24 \cdot 10^{-38}$), flagged as the only
        numerical bound appearing verbatim in
        \cite{Sawin2026Remarks};
  \item \tname{sawin_refinement_reported} ($\delta = 0.0318$),
        flagged as not literally present in either formal PDF.
\end{itemize}

Reproducing $0.014$ or $0.0318$ would require a different artifact
working from a different (and in the first case unpublished) source;
that is outside the scope claimed here.

\subsection{This artifact does NOT improve the published bound}

We made no attempt to optimise the choice of $T$, $S$, $L_T$ or the
inner parameter $k$ to obtain a larger $\delta_{\text{excess}}$. The
explicit choice of \cite[\S2.1]{Sawin2026Remarks} is what we encode and
reproduce; the optimisation problem of finding $(T, S, k)$ with larger
admissible $\delta$ remains open and is out of scope.
