% Section 7: Reproducibility

\subsection{One-line reproduction}

\begin{quote}\ttfamily
git clone https://github.com/Flamehaven-Labs/openai-erdos-eq22-reproduction\\
cd openai-erdos-eq22-reproduction\\
pip install -e ".[dev]"\\
python -m erdos\_ant.verify
\end{quote}

\noindent
Expected terminal output:

\begin{quote}\ttfamily
Verdict: PASS\\
Checks: 21/21 passed\\
eq (2.2) exponent excess: 6.2391e-38 (published \textasciitilde 6.24e-38, rel.err 0.0001)\\
(frozen-report mode: tracked evidence not written; pass --write-evidence to refresh)
\end{quote}

\noindent
By default the command does not write to disk; the working tree stays
clean. Release maintainers pass \texttt{--write-evidence} to refresh the
tracked files
\path{reports/verification_result.json} and
\path{reports/verification_report.md}.

\subsection{Pinned environment}

\begin{tabular}{ll}
\toprule
Item & Value \\
\midrule
Repository & \url{https://github.com/Flamehaven-Labs/openai-erdos-eq22-reproduction} \\
Version (paper source) & v0.2.2 \\
Tagged paper revisions & v0.1.3 (first paper-bearing), v0.1.4 (placeholder fill-in), v0.2.0 (positioning pass), v0.2.1 (source-alignment audit), v0.2.2 (public naming alignment) \\
Commit hash (v0.1.3 release tag) & \texttt{c8fe529} \\
Python & 3.11 and 3.12 (CI-verified) \\
numpy & $\geq 1.26$ \\
mpmath & $\geq 1.3$ \\
Test count & $60$ unit tests $+$ $21$ verifier checks \\
CI matrix & Ubuntu $\times$ Windows $\times$ Python 3.11 / 3.12 \\
Licence & MIT \\
DOI (predecessor v0.1.1, source-only) & \href{https://doi.org/10.5281/zenodo.20366884}{10.5281/zenodo.20366884} \\
DOI (v0.1.3, first paper-bearing) & \href{https://doi.org/10.5281/zenodo.20377950}{10.5281/zenodo.20377950} \\
\bottomrule
\end{tabular}

\subsection{Supplementary automated scanners}

In addition to its own test suite the source tree was run through
three automated scanners; their outputs are recorded at
\path{reports/TRIPLE_INSPECTION_REPORT.md} in the repository. We list
them here for transparency and explicitly \emph{not} as third-party
endorsement: one of the three (AI-SLOP-Detector) is maintained by the
same author as this artifact.

\begin{tabular}{llll}
\toprule
Scanner & Affiliation & Result & Headline metric \\
\midrule
AI-SLOP-Detector v3.7.5 & in-house & \texttt{clean} (6/6 files) & weighted deficit $= 2.83$ (threshold $30$) \\
SPAR Framework v0.5.0 & external & \texttt{ACCEPT} & score $100/100$, claim drift $= 0$ \\
SIDRCE SaaS v1.1.15 & external & \texttt{CERTIFIED} & $\Omega = 0.9289$, trace chain verified \\
\bottomrule
\end{tabular}

None of these tools performs mathematical peer review. Their scope is
restricted to source-level pattern checks (structural slop, claim /
documentation drift, code integrity); the substantive correctness of
the eq.~(2.2) reproduction is not within their remit. See
\S\ref{sec:limits} for the bound on what these scanners can and cannot
attest to.

\subsection{Citation}

A \texttt{CITATION.cff} file in the repository root provides citation
metadata in the Citation File Format v1.2 standard, recognised by
Zenodo, GitHub, and most citation managers. The recommended citation
for a specific tagged release is the Zenodo DOI associated with that
tag.
